---
title: "my vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753Weng0006)
```


## Introduction
This package contains some functions that I have learned this semester
This vignette presents the 4 functions I have learned this semester

## First function

scatterhist is a function that will make scatter histogram
 
```{r}
MATH4753Weng0006::scatterhist(ddt$LENGTH,ddt$WEIGHT)

```
 
## Second function

mymult is a function that will make multinomial probability distribution 
 
```{r}
MATH4753Weng0006::mymult(iter=1000,n=10,p=c(1,2,3,4,2)/12)

```
 
 
## Third function

 mymaxlik is a function that will make maximum likelihood estimates
```{r}
loggamma=function(x,param) log(dgamma(x,log = FALSE, shape = 2,rate =param ))
MATH4753Weng0006::mymaxlik(x=c(9,9,1,9,9,9),param=seq(0,1,length=1000),lfun=loggamma)
```

 
## fourth function 

myncurve will display the dnorm curve, shaded area between the curve and x axis from negative infinity to x=a,  
 
```{r}
MATH4753Weng0006::myncurve(5,10,6)
```
 
 
 
 
 
 
 
 
 
